Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-04 paper/paper.qmd
committing testing scripts and changes to paper.qmd

- “If the election were held today, would you vote for [Candidate A] or [Candidate B]?” 
- “How strongly do you support [Candidate]?” (e.g., on a scale of 1 to 10, or strongly, somewhat, undecided)
- “Do you support [Policy A] proposed by [Candidate A] or [Policy B] proposed by [Candidate B]?”

@@

Each respondent’s answers and demographic details are grouped and saved in a structured database. Pollsters then clean the data by checking for inconsistencies, removing incomplete responses, and addressing non-responses. Pollsters also perform weighting to ensure the representativeness of data collected, details of weighting are further explained in {appendix 1}.

@@

```
This variability in numeric grade highlights the diversity in polling quality within our dataset. The presence of peaks suggests that some pollsters consistently receive higher ratings, likely due to their use of more rigorous methods or transparent reporting standards. Conversely, the valleys in the distribution may indicate fewer polls from sources with lower numeric grades, reflecting a potential tendency for lower-quality polls to be less prevalent or less frequently conducted. By accounting for numeric grade, we can improve the accuracy of predictions by emphasizing data from more reliable sources. This consideration is crucial, as polling quality can impact the stability of the model’s forecasts, especially in closely contested states where polling accuracy is essential for reliable predictions.

@@

# Pollster methodology overview and evaluation: NYT/Siena College

>>>>

- “If the election were held today, would you vote for Candidate A or Candidate B?” 
- “How strongly do you support Candidate?” (e.g., on a scale of 1 to 10, or strongly, somewhat, undecided)
- “Do you support Policy A proposed by Candidate A or Policy B proposed by Candidate B?”

@@

Each respondent’s answers and demographic details are grouped and saved in a structured database. Pollsters then clean the data by checking for inconsistencies, removing incomplete responses, and addressing non-responses. Pollsters also perform weighting to ensure the representativeness of data collected, details of weighting are further explained in @sec-pollster-methodology.

@@

```
This variability in numeric grade highlights the diversity in polling quality within our dataset. The presence of peaks suggests that some pollsters consistently receive higher ratings, likely due to their use of more rigorous methods or transparent reporting standards. Conversely, the valleys in the distribution may indicate fewer polls from sources with lower numeric grades, reflecting a potential tendency for lower-quality polls to be less prevalent or less frequently conducted. By accounting for numeric grade, we can improve the accuracy of predictions by emphasizing data from more reliable sources. This consideration is crucial, as polling quality can impact the stability of the model’s forecasts, especially in closely contested states where polling accuracy is essential for reliable predictions.
\newpage

@@

# Pollster methodology overview and evaluation: NYT/Siena College {#sec-pollster-methodology}
